A higher order approximate static condensation method for multi-material diffusion problems

### 2018-11-27 asc.tex
Modify SPD proof + add minor fixes to theoretical part

\DeclareMathOperator{\Ker}{Ker}

% listings
%\usepackage{listings}
%\lstset{
%	basicstyle=\linespread{.95}\footnotesize\ttfamily\color{black},
%	keywordstyle=\color{green!40!black},
%	emphstyle=\bfseries\color{green!40!black},
%	commentstyle=\itshape\color{purple!40!black},
%	identifierstyle=\color{blue!30!black},
%	showstringspaces=false,
%	stringstyle=\color{orange},
%	numbers=left,
%	tabsize=2,
%	breaklines=true,
%	breakatwhitespace=true,
%	language=C++
%}

@@

@@

\title{A higher order approximate static condensation method for multi-material problems}
\author{
Alexander Zhiliakov\thanks{Department of Mathematics, University of Houston, Houston, Texas 77204 (alex@math.uh.edu).}
\and Daniil Svyatskiy\thanks{Los Alamos National Laboratory, Los Alamos,
New Mexico, USA (dasvyat@lanl.gov).}
\and
Maxim Olshanskii\thanks{Department of Mathematics, University of Houston, Houston, Texas 77204 (molshan@math.uh.edu); Partially supported by NSF through grant  DMS-1717516.}
}

@@

\section{Introduction}
 Multi-phase and multi-material processes are ubiquitous in nature and engineering.
 Mathematical models of such processes are often formulated in terms of systems of partial differential equations with discontinuous coefficients and interface conditions on time-dependent internal boundaries.
 Due to their high complexity, these models   resist analytical treatment, and hence numerical simulations became an indispensable tool for solving the models and gaining insights into underlying phenomena.

@@

In this report, we devise  a higher order method for the numerical solution of the diffusion problem with discontinuous  coefficients on a general polyhedral mesh, which does not respect the position of multi-material interfaces.  The method builds upon the approximate static condensation (ASC) algorithm first  proposed in ~\cite{kikinzon2017approximate}; it admits high-contrast diffusion coefficients and discontinuous reconstruction of the interfaces as typical for the volume/moment-of-fluid method. The ASC approach uses the formulation of the interface diffusion problem as a system of local inter-cell problems  coupled through the concentration values and fluxes on the cell faces. This face concentration serves as the new primal unknown and it is further approximated by piecewise  polynomial functions defined on all faces of the global (unfitted polygonal) mesh. The original paper ~\cite{kikinzon2017approximate} considered $P_0$ (piecewise constant) approximation to the face concentration, while the present study introduces higher order polynomials for this purpose.
Although the latter potentially leads to more accurate results  (and in some cases we shall see that it provides convergent results, when the $P_0$ version fails), it also raises some questions about stability and robustness, which we address in the present report.

@@

Denote by $\bfaces$ the collection of all faces of the macro-mesh $\bmesh$. We shall distinct between the subset of internal and external faces,  $\bfaces = \bfaces[int] \cup \bfaces[ext]$\footnote{For the sake of  notation, we shall use~$\bfaces$ to denote both the set of elements and the corresponding domain formed by their union~$\cup_{F\in \bfaces} \bar{F}$; same for $\bfaces[int]$, $\bfaces[ext]$ and other collections of mesh elements introduced later in the text. The meaning should be clear from a context.}.
Introducing the new unknown \toDiscuss{$\lambda \in \HHalfSpace[\bfaces]$}, we reformulate \eqref{dual}--\eqref{dual:bc} as a system of local problems coupled through the boundary data
and flux continuity condition:
\begin{eqnarray}
	\arraycolsep=2pt\def\arraystretch{1.5}
	\left\{\begin{array}{rcrccl}
		\vect K^{-1}\,\vect u                    & + & \nabla\,p & = & 0       &\quad\text{in } \bcell, \\
		\nabla\cdot\vect u                       & + & c\,p      & = & f       &\quad\text{in } \bcell, \\
		                                         &   & p         & = & \lambda &\quad\text{on } \partial\bcell, %\label{dual_mini:trace}
	\end{array}\right. 
	& \qquad \forall~\bcell\in\bmesh, \label{dual_mini} \\
	\llbracket\vect u \cdot \hat{\vect n}\rrbracket = 0\quad\:\:\text{on } F,\:\:\:\:
	& \qquad\quad \forall~F\in\bfaces[int]. \label{flux_cond}
\end{eqnarray}
Here $\hat{\vect n}$ denotes a normal vector to the face $F\in\bfaces[int]$ and $\llbracket \vect u\cdot\hat{\vect n} \rrbracket$ is the jump of the normal flux across $F$. On the outer boundary $\partial\Omega$ we assume \eqref{dual:bc}.

@@

Before we go into details of the method, we note that $\lambda$ can also  be observed as the Lagrange multiplier corresponding to the normal flux condition~\eqref{flux_cond}. The problem \eqref{dual_mini}--\eqref{flux_cond} can be formulated in the weak form: \toDiscuss{Find}  $\vect u \in \bigotimes\limits_{\bcell\in\bmesh}\HDivNodeSpace[\bcell]$, $ p\in\LTwoSpace$, $\lambda \in \bigotimes\limits_{\bface\in\bfaces[int]}\HHalfSpace$ such that
\begin{equation}\label{weak_form}
	\begin{split}
		\int_{\Omega} \vect K^{-1}\,\vect u\cdot\vect v \diff \vect x - \sum_{\bcell\in\bmesh}\int_\bcell p\,\nabla\cdot\vect v \diff \vect x + \sum_{\bface\in\bfaces[int]}\int_{\bface} \lambda\,\llbracket\vect v\cdot\hat{\vect n}\rrbracket \diff l &= -\int_{\partial\Omega_D} g_D\,\vect v\cdot\hat{\vect n} \diff l, \\
		\sum_{\bcell\in\bmesh}\int_\bcell \nabla\cdot\vect u\,q \diff \vect x + \int_\Omega c\,p\,q \diff \vect x &= \int_\Omega f\,q \diff \vect x, \\
		\sum_{\bface\in\bfaces[int]}\int_{\bface} \llbracket\vect u\cdot\hat{\vect n}\rrbracket\,\mu \diff l &= 0
\end{split}
\end{equation}
for all $\vect v \in \bigotimes\limits_{\bcell\in\bmesh}\HDivNodeSpace[\bcell]$, $q \in \LTwoSpace[\Omega]$, and $\mu \in \bigotimes\limits_{\bface\in\bfaces[int]}\HHalfSpace$\footnotemark{}.

\footnotetext{Here we assumed~$g_N \equiv 0$. The case $g_N \ne 0$ is handled via the change of variables~$\vect u = \vect u_0 + \vect u_N$, $\vect u_0\cdot\hat{\vect n} = 0$ and $\vect u_N\cdot\hat{\vect n} = g_N$ on~$\partial\Omega_N$ with some fixed~$\vect u_N \in \bigotimes\limits_{\bcell\in\bmesh}\HDivSpace[\bcell]$.}

%Find  $\vect u  \in \bigotimes\limits_{\bcell\in\bmesh}\HDivSpace[\bcell]$, $ p\in\LTwoSpace[\Omega]$, $\lambda\in H^{\frac12}(\bfaces[int])$ such that $\vect u\cdot\hat{\vect n}=g_N$ on $\partial\Omega_N$ and
%\begin{equation}\label{weak_form}
%		\begin{split}
%				\int_{\Omega} \vect K^{-1}\,\vect u\cdot\vect v \diff \vect x - \sum_{\bcell\in\bmesh}\int_\bcell p\,\nabla\cdot\vect v \diff \vect x +\int_{\bfaces[int]} \lambda\,\left[\vect v\cdot\hat{\vect n}\right] \diff \vect l &- \int_{\bfaces[int]}\left[\vect u\cdot\hat{\vect n}\right]\mu\diff \vect l, \\
%				+\sum_{\bcell\in\bmesh}\int_\bcell \nabla\cdot\vect u\,q \diff \vect x + \int_\Omega c\,p\,q \diff \vect x &= \int_\Omega f\,q \diff \vect x-\int_{\partial\Omega_D}\vect v\cdot\hat{\vect n}g_D\diff \vect l
%		\end{split}
%\end{equation}
%for all $\vect v  \in \bigotimes\limits_{\bcell\in\bmesh}\HDivSpace[\bcell]$, $ q\in\LTwoSpace[\Omega]$, $\mu\in H^{\frac12}(\bfaces[int])$.

@@

We shall discretize \eqref{dual_mini} in $T$ in terms of average fluxes assigned to each face from $\mfaces(T)$,
we denote the corresponding vector by ${\vect u}_\mmesh\in\mathbb{R}^{n_f}$, \toDiscuss{$n_f=\#\mfaces(T)$},  and concentration values assigned to each cell ${\tau \in \mmesh(T)}$, we denote the corresponding vector by ${\vect p}_\mmesh\in\mathbb{R}^{n_p}$, $n_p=\#\mmesh(T)$. The given data is the source term vector ${\vect f}_\mmesh\in \mathbb{R}^{n_p}$ and the concentration values $\lambda$ on the boundary of $T$.
To approximate this boundary data \emph{for the local problem}, we introduce the vector
${\vect \lambda}_\mmesh\in\mathbb{R}^{n_\lambda}$, $n_\lambda=\#\mfaces[ext](T)$,
where we assign one averaged concentration value for each $f\in\mfaces[ext](T)$, so that ${\vect \lambda}_\mmesh$ can be seen as a piecewise-constant approximation of $\lambda$ with respect to the subdivision of $\partial T$ into the faces of the local mesh $\mmesh$.

@@

Given the above definition of the degrees of freedom on the local mesh we apply the mimetic finite difference (MFD) method from~\cite{lipnikov2014mimetic}. The method leads to the following system of equations with the matrix having the block structure:
	\begin{equation}\label{local}
		\begin{pmatrix}
			\phantom{-}\vect M_\mmesh & \vect B^T_\mmesh \\
			-\vect B_\mmesh & \vect \Sigma_\mmesh
		\end{pmatrix}
		\begin{pmatrix}
			{\vect u}_\mmesh \\
			{\vect p}_\mmesh
		\end{pmatrix}
		=
		\begin{pmatrix}
			\vect E_\mmesh\,\vect C_\mmesh\,{\vect \lambda}_\mmesh \\
			{\vect f}_\mmesh
		\end{pmatrix}.
	\end{equation}
Here $\vect M_\mmesh$, $\vect\Sigma_\mmesh$, $\vect B^T_\mmesh$, $(-\vect B_\mmesh)$ are vector-mass, mass, gradient and divergence matrices, respectively.
\toDiscuss{$(-\vect C_\mmesh)$} is a diagonal scaling matrix. i.e. the mass matrix for ${\vect \lambda}_\mmesh$ unknowns;
$\vect E_\mmesh \in \toDiscuss{\mathbb{R}^{n_f \times n_\lambda}}$ is a rectangular matrix with 0 and 1 entries which sparsifies a vector from  $\mathbb{R}^{n_{\lambda}}$
to a vector from  $\mathbb{R}^{n_{f}}$.
For the details on MFD and accurate definition of the matrices we refer to \cite{lipnikov2014mimetic,MFDbook}.
Here we need the property that  $\vect B_\mmesh$ has a full row rank, and $\vect M_\mmesh = \vect M^T_\mmesh$ is positive definite.

@@

Next, we should use the continuity of flux condition \eqref{flux_cond} and boundary conditions to obtain a complete system for ${\vect u}^\text{ext}_\mmesh$ and ${\vect \lambda}_\mmesh$. However, we cannot do this in a straightforward way, since the discontinuity of material interfaces across the macro-mesh faces may lead to a mismatch of discrete fluxes from two sides of $F\in\bfaces[int]$, including different space dimensions.
Therefore, we shall enforce the flux continuity condition in the spirit of the mortar finite element method~\cite{mortar} using the space of function defined on $\bfaces[int]$, which are polynomials of degree at most $n$ on every $F\in\bfaces[int]$, an analog of the Lagrange multiplier space in the mortar method:
\[
\Lambda=\left\{\lambda\in \LTwoSpace[\toDiscuss{\bfaces[int]}]\,:\, \lambda\in P_n~\text{for any}~F\in\bfaces[int]\right\}.
\]

@@

For $F \in \bfaces[int]$ shared by two polygonal cells~$\bcell^\pm\in \bmesh$  denote by~$\mfaces_F(T^\pm) \subset \mfaces_{\text{ext}}(T^\pm)$ the subsets of mini-faces that belong to the macro-face~$F$ from each side. Let $\nu_F \coloneqq \max\,\{ \#\,\mfaces_F(T^+),\,\#\,\mfaces_F(T^-) \}$. \toDiscuss{We} set~$\bfaces_\bcell \subset \bfaces$ to be a subset of macro-faces forming the boundary of a cell~$T$. With each face $F \in \bfaces_\bcell$ we associate~$\min\,\{ n+1, \nu_F \}$ degrees of freedom~\eqref{asc_dofs} in the $\Lambda$ space. The local and global number of d.o.f. are
\[
	n_\bcell = \sum_{F \in \bfaces_\bcell} \min\,\{ n+1, \nu_F \} \quad\text{and}\quad
	n_\bmesh = \sum_{F \in \bfaces} \min\,\{ n+1, \nu_F \},
\]
respectively.

Further denote by~${{\vect \lambda}_\bcell \in \Rn{n_\bcell}}$ a vector of d.o.f. for elements of $\Lambda$ associated with all macro-faces spanning the boundary of~$\bcell$. We need a correspondence between elements of $\Lambda$ and local \toDiscuss{edge elements} $\vect \lambda_\mmesh$ used as boundary data in local problem \eqref{local}.
This corresponding is given by the interpolation matrix $ \vect R_\mmesh$,
\begin{equation}\label{asc_lambda}
	{\vect \lambda}_\mmesh = \vect R_\mmesh\,{\vect \lambda}_\bcell,
\end{equation}
where ${\vect \lambda}_\mmesh$ is effectively a piecewise constant approximation of ${\vect \lambda}_\bcell$ on $\mfaces_{\text{ext}}(T)$.
Using this in \eqref{mini_flux_dofs}, we get
	\begin{equation}\label{asc_flux_lambda}
		{\vect u}^\text{ext}_\mmesh = \vect A_\mmesh\,\vect C_\mmesh\,\vect R_\mmesh\,{\vect \lambda}_\bcell + {\vect a}_\mmesh.
	\end{equation}
	%The interpolating matrix~$\vect R_\mmesh$ is completely defined by~$n$ and boundary mini\,faces~$\mfaces[ext]$ of~$\mmesh$.
If we find the mortar vector ~${\vect \lambda}_\bcell$, we recover the local approximation to the \toDiscuss{edge} concentration, i.e. ${\vect \lambda}_\mmesh$, from~\eqref{asc_lambda}.
Further we solve numerically local subproblems in~\eqref{dual_mini} applying the mimetic FD method. This completes the solution algorithm for \eqref{dual}.

The dimension of the $\Lambda$ space is~$n_\bmesh$, i.e. $(n+1)$ or less unknowns for each face~${F \in \bfaces}$.
To obtain the system of $n_\bmesh$ equations, we enforce the weak continuity of the moments of  fluxes  on each internal macro-face
\begin{equation}\label{flux_cont}
	\int_F \vect u|_{\bcell^+}\cdot\hat{\vect n}\,s_i \diff l = \int_F \vect u|_{\bcell^-}\cdot\hat{\vect n}\,s_i \diff l, \quad i = 0, \dots, n, \quad \text{for each } F \in \bfaces[int],
\end{equation}
with \toDiscuss{$\big(\vect u|_{\bcell^+}\cdot\hat{\vect n}\big)(\vect x) = u^\text{ext}_\mmesh(f)\,|f|$}, if $\vect x \in f$ for $f\in\mfaces_F(T^+)$, and $u^\text{ext}_\mmesh(f) \in \vect u^\text{ext}_\mmesh$ is the local flux assigned to $f$. Similar definition applies to $\vect u|_{\bcell^-}$. 	
This and~\eqref{asc_flux_lambda} result in the linear algebraic system
\begin{equation}\label{asc_system}
	\vect S_\bmesh\,{\vect \lambda}_\bmesh = {\vect b}_\bmesh,
\end{equation}
with	$\vect S_\bmesh \in \Rn{n_\bmesh \times n_\bmesh}, {\vect \lambda}_\bmesh, {\vect b}_\bmesh \in \Rn{n_\bmesh}$.
Neumann boundary condition in~\eqref{dual:bc} is handled in the similar way, and Dirichlet boundary data in~\eqref{dual:bc} is enforced strongly in~\eqref{asc_system}.

@@

We define $\vect R_\mmesh$ locally for any fixed $\bcell\in\bmesh$. Let us enumerate all faces of the given $T$ by index $j$. For example, $j=1,\dots,4$ for the polygonal cell in Figure~\ref{fig:asc_dofs:asc1:mmc}. For each $j$, index $i$ enumerates mini-faces from $\mfaces[ext](T)$ belonging to the macro-face $j$. For example, $i\in\{1,2,3\}$ for $j=1$ and $i\in\{1\}$ for $j=4$ for the same example in Figure~\ref{fig:asc_dofs:asc1:mmc}. Further, denote by $\lambda_{j\,i}(\mmesh)$ the local d.o.f. assigned to the $i$-th mini-face belonging to the $j$-th macro-face, and by $\lambda_{j}(T)$, $\lambda_{j}'(T)$ two moments defining an element from $\Lambda$ on the $j$-th macro-face \big(see Figure~\ref{fig:asc_dofs:asc1:mmc})\big) so that
we have for $\lambda\in\Lambda$,
\begin{equation}\label{lambda_intermsof_moments}
	{\lambda}\big({\vect r}(t)\big) = \lambda_{j}'(T)|F|\,t + \left( \lambda_{j}(T) - \frac{\lambda_{j}'(T)\,|F|}{2} \right),\qquad  F\in\bfaces[int],
\end{equation}
where $t\in(0,1)$ and ${\vect r}\::\:\left(0,1\right) \rightarrow F$ is the affine parametrization of $F$, which has index $j$ among macro-faces of $T$.

>>>>

\DeclareMathOperator{\Ker}{ker}
\DeclareMathOperator{\Dim}{dim}

@@

\title{A higher order approximate static condensation method for multi-material diffusion problems}
\author{
	Alexander Zhiliakov\thanks{Department of Mathematics, University of Houston, Houston, Texas 77204 (alex@math.uh.edu).}
	\and Daniil Svyatskiy\thanks{Los Alamos National Laboratory, Los Alamos,
		New Mexico, USA (dasvyat@lanl.gov).}
	\and
	Maxim Olshanskii\thanks{Department of Mathematics, University of Houston, Houston, Texas 77204 (molshan@math.uh.edu); Partially supported by NSF through grant  DMS-1717516.}
	\and Evgeny Kikinzon \thanks{Los Alamos National Laboratory, Los Alamos,
		New Mexico, USA (kikinzon@lanl.gov).}
	\and Mikhail Shashkov\thanks{Los Alamos National Laboratory, Los Alamos,
		New Mexico, USA (shashkov@lanl.gov).}
}

@@

@@

	\section{Introduction}

	Multi-phase and multi-material processes are ubiquitous in nature and engineering.
	Mathematical models of such processes are often formulated in terms of systems of partial differential equations with discontinuous coefficients and interface conditions on time-dependent internal boundaries.
	Due to their high complexity, these models   resist analytical treatment, and hence numerical simulations became an indispensable tool for solving the models and gaining insights into underlying phenomena.

@@

	In this report, we devise  a higher order method for the numerical solution of the diffusion problem with discontinuous  coefficients on a general polyhedral mesh, which does not respect the position of multi-material interfaces.  The method builds upon the approximate static condensation (ASC) algorithm first proposed in~\cite{kikinzon2017approximate}; it admits high-contrast diffusion coefficients and discontinuous reconstruction of the interfaces as typical for the volume/moment-of-fluid method. The ASC approach uses the formulation of the interface diffusion problem as a system of local inter-cell problems  coupled through the concentration values and fluxes on the cell faces. This face concentration serves as the new primal unknown and it is further approximated by piecewise  polynomial functions defined on all faces of the global (unfitted polygonal) mesh. The original paper ~\cite{kikinzon2017approximate} considered $P_0$ (piecewise constant) approximation to the face concentration, while the present study introduces higher order polynomials for this purpose.
	Although the latter potentially leads to more accurate results  (and in some cases we shall see that it provides convergent results, when the $P_0$ version fails), it also raises some questions about stability and robustness, which we address in the present report.

@@

	Denote by $\bfaces$ the collection of all faces of the macro-mesh $\bmesh$. We shall distinct between the subset of internal and external faces,  $\bfaces = \bfaces[int] \cup \bfaces[ext]$\footnote{For the sake of  notation, we shall use~$\bfaces$ to denote both the set of elements and the corresponding domain formed by their union~$\cup_{F\in \bfaces} \bar{F}$; same for $\bfaces[int]$, $\bfaces[ext]$ and other collections of mesh elements introduced later in the text. The meaning should be clear from a context.}.
	Introducing the new unknown $\lambda \in \HHalfSpace[\bfaces]$, we reformulate \eqref{dual}--\eqref{dual:bc} as a system of local problems coupled through the boundary data
	and flux continuity condition:
	\begin{eqnarray}
		\arraycolsep=2pt\def\arraystretch{1.5}
		\left\{\begin{array}{rcrccl}
			\vect K^{-1}\,\vect u                    & + & \nabla\,p & = & 0       &\quad\text{in } \bcell, \\
			\nabla\cdot\vect u                       & + & c\,p      & = & f       &\quad\text{in } \bcell, \\
			                                         &   & p         & = & \lambda &\quad\text{on } \partial\bcell, %\label{dual_mini:trace}
		\end{array}\right. 
		& \qquad \forall~\bcell\in\bmesh, \label{dual_mini} \\
		\llbracket\vect u \cdot \hat{\vect n}\rrbracket = 0\quad\:\:\text{on } F,\:\:\:\:
		& \qquad\quad \forall~F\in\bfaces[int]. \label{flux_cond}
	\end{eqnarray}
	Here $\hat{\vect n}$ denotes a normal vector to the face $F\in\bfaces[int]$ and $\llbracket \vect u\cdot\hat{\vect n} \rrbracket$ is the jump of the normal flux across $F$. On the outer boundary $\partial\Omega$ we assume \eqref{dual:bc}.

@@

	Before we go into details of the method, we note that $\lambda$ can also  be observed as the Lagrange multiplier corresponding to the normal flux condition~\eqref{flux_cond}. The problem \eqref{dual_mini}--\eqref{flux_cond} can be formulated in the weak form: Find $\vect u \in \bigotimes\limits_{\bcell\in\bmesh}\HDivSpace[\bcell]$ s.t. $\vect u \cdot \hat{\vect n} = g_N$ on $\partial\Omega_N$, $ p\in\LTwoSpace$, $\lambda\in\HHalfSpace[{\bfaces[int]}]$ such that
	\begin{equation}\label{weak_form}
		\begin{split}
			\int_{\Omega} \vect K^{-1}\,\vect u\cdot\vect v \diff \vect x - \sum_{\bcell\in\bmesh}\int_\bcell p\,\nabla\cdot\vect v \diff \vect x + \sum_{\bface\in\bfaces[int]}\int_{\bface} \lambda\,\llbracket\vect v\cdot\hat{\vect n}\rrbracket \diff l &= -\int_{\partial\Omega_D} g_D\,\vect v\cdot\hat{\vect n} \diff l, \\
			\sum_{\bcell\in\bmesh}\int_\bcell \nabla\cdot\vect u\,q \diff \vect x + \int_\Omega c\,p\,q \diff \vect x &= \int_\Omega f\,q \diff \vect x, \\
			\sum_{\bface\in\bfaces[int]}\int_{\bface} \llbracket\vect u\cdot\hat{\vect n}\rrbracket\,\mu \diff l &= 0
		\end{split}
	\end{equation}
	for all $\vect v \in \bigotimes\limits_{\bcell\in\bmesh}\HDivSpace[\bcell]$ s.t. $\vect v \cdot \hat{\vect n} = 0$ on $\partial\Omega_N$, $q \in \LTwoSpace[\Omega]$, and $\mu \in \HHalfSpace[{\bfaces[int]}]$.

	%	\footnotetext{Here we assumed~$g_N \equiv 0$. The case $g_N \ne 0$ is handled via the change of variables~$\vect u = \vect u_0 + \vect u_N$, $\vect u_0\cdot\hat{\vect n} = 0$ and $\vect u_N\cdot\hat{\vect n} = g_N$ on~$\partial\Omega_N$ with some fixed~$\vect u_N \in \bigotimes\limits_{\bcell\in\bmesh}\HDivSpace[\bcell]$.}
	%Find  $\vect u  \in \bigotimes\limits_{\bcell\in\bmesh}\HDivSpace[\bcell]$, $ p\in\LTwoSpace[\Omega]$, $\lambda\in H^{\frac12}(\bfaces[int])$ such that $\vect u\cdot\hat{\vect n}=g_N$ on $\partial\Omega_N$ and
	%\begin{equation}\label{weak_form}
	%		\begin{split}
	%				\int_{\Omega} \vect K^{-1}\,\vect u\cdot\vect v \diff \vect x - \sum_{\bcell\in\bmesh}\int_\bcell p\,\nabla\cdot\vect v \diff \vect x +\int_{\bfaces[int]} \lambda\,\left[\vect v\cdot\hat{\vect n}\right] \diff \vect l &- \int_{\bfaces[int]}\left[\vect u\cdot\hat{\vect n}\right]\mu\diff \vect l, \\
	%				+\sum_{\bcell\in\bmesh}\int_\bcell \nabla\cdot\vect u\,q \diff \vect x + \int_\Omega c\,p\,q \diff \vect x &= \int_\Omega f\,q \diff \vect x-\int_{\partial\Omega_D}\vect v\cdot\hat{\vect n}g_D\diff \vect l
	%		\end{split}
	%\end{equation}
	%for all $\vect v  \in \bigotimes\limits_{\bcell\in\bmesh}\HDivSpace[\bcell]$, $ q\in\LTwoSpace[\Omega]$, $\mu\in H^{\frac12}(\bfaces[int])$.

@@

	We shall discretize \eqref{dual_mini} in $T$ in terms of average fluxes assigned to each face from $\mfaces(T)$,
	we denote the corresponding vector by ${\vect u}_\mmesh\in\mathbb{R}^{n_f}$, $n_f=\#\mfaces(T)$,  and concentration values assigned to each cell ${\tau \in \mmesh(T)}$, we denote the corresponding vector by ${\vect p}_\mmesh\in\mathbb{R}^{n_p}$, $n_p=\#\mmesh(T)$. The given data is the source term vector ${\vect f}_\mmesh\in \mathbb{R}^{n_p}$ and the concentration values $\lambda$ on the boundary of $T$.
	To approximate this boundary data \emph{for the local problem}, we introduce the vector
	${\vect \lambda}_\mmesh\in\mathbb{R}^{n_\lambda}$, $n_\lambda=\#\mfaces[ext](T)$,
	where we assign one averaged concentration value for each $f\in\mfaces[ext](T)$, so that ${\vect \lambda}_\mmesh$ can be seen as a piecewise-constant approximation of $\lambda$ with respect to the subdivision of $\partial T$ into the faces of the local mesh $\mmesh$.

@@

	Given the above definition of the degrees of freedom on the local mesh we apply the mimetic finite difference (MFD) method from~\cite{lipnikov2014mimetic}. The method leads to the following system of equations with the matrix having the block structure:
	\begin{equation}\label{local}
		\begin{pmatrix}
			\phantom{-}\vect M_\mmesh & \vect B^T_\mmesh \\
			-\vect B_\mmesh & \vect \Sigma_\mmesh
		\end{pmatrix}
		\begin{pmatrix}
			{\vect u}_\mmesh \\
			{\vect p}_\mmesh
		\end{pmatrix}
		=
		\begin{pmatrix}
			\vect E_\mmesh\,\vect C_\mmesh\,{\vect \lambda}_\mmesh \\
			{\vect f}_\mmesh
		\end{pmatrix}.
	\end{equation}
	Here $\vect M_\mmesh$, $\vect\Sigma_\mmesh$, $\vect B^T_\mmesh$, $-\vect B_\mmesh$ are vector-mass, mass, gradient and divergence matrices, respectively. $-\vect C_\mmesh$ is a diagonal scaling matrix. i.e. the mass matrix for ${\vect \lambda}_\mmesh$ unknowns;
	$\vect E_\mmesh \in \mathbb{R}^{n_f \times n_\lambda}$ is a rectangular matrix with 0 and 1 entries which sparsifies a vector from  $\mathbb{R}^{n_{\lambda}}$
	to a vector from  $\mathbb{R}^{n_{f}}$.
	For the details on MFD and accurate definition of the matrices we refer to \cite{lipnikov2014mimetic,MFDbook}.
	Here we need the property that  $\vect B_\mmesh$ has a full row rank, and $\vect M_\mmesh = \vect M^T_\mmesh$ is positive definite.

@@

	Next, we should use the continuity of flux condition \eqref{flux_cond} and boundary conditions to obtain a complete system for ${\vect u}^\text{ext}_\mmesh$ and ${\vect \lambda}_\mmesh$. However, we cannot do this in a straightforward way, since the discontinuity of material interfaces across the macro-mesh faces may lead to a mismatch of discrete fluxes from two sides of $F\in\bfaces[int]$, including different space dimensions.
	Therefore, we shall enforce the flux continuity condition in the spirit of the mortar finite element method~\cite{mortar} using the space of function defined on $\bfaces[int]$, which are polynomials of degree at most $n$ on every $F\in\bfaces[int]$, an analog of the Lagrange multiplier space in the mortar method:
	\[
		\Lambda=\left\{\lambda\in \LTwoSpace[{\bfaces[int]}]\,:\, \lambda\in P_n~\text{for any}~F\in\bfaces[int]\right\}.
	\]

@@

	For $F \in \bfaces[int]$ shared by two polygonal cells~$\bcell^\pm\in \bmesh$  denote by~$\mfaces_F(T^\pm) \subset \mfaces_{\text{ext}}(T^\pm)$ the subsets of mini-faces that belong to the macro-face~$F$ from each side. Let $\nu_F \coloneqq \max\,\{ \#\,\mfaces_F(T^+),\,\#\,\mfaces_F(T^-) \}$. We set~$\bfaces_\bcell \subset \bfaces$ to be the subset of macro-faces forming the boundary of a cell~$T$. With each face $F \in \bfaces_\bcell$ we associate~$\min\,\{ n+1, \nu_F \}$ degrees of freedom~\eqref{asc_dofs} in the $\Lambda$ space. The local and global number of d.o.f. are
	\[
		n_\bcell = \sum_{F \in \bfaces_\bcell} \min\,\{ n+1, \nu_F \} \quad\text{and}\quad
		n_\bmesh = \sum_{F \in \bfaces} \min\,\{ n+1, \nu_F \},
	\]
	respectively.

	Further denote by~${{\vect \lambda}_\bcell \in \Rn{n_\bcell}}$ a vector of d.o.f. for elements of $\Lambda$ associated with all macro-faces spanning the boundary of~$\bcell$. We need a correspondence between elements of $\Lambda$ and local face elements $\vect \lambda_\mmesh$ used as boundary data in local problem \eqref{local}.
	This corresponding is given by the interpolation matrix $ \vect R_\mmesh$,
	\begin{equation}\label{asc_lambda}
		{\vect \lambda}_\mmesh = \vect R_\mmesh\,{\vect \lambda}_\bcell,
	\end{equation}
	where ${\vect \lambda}_\mmesh$ is effectively a piecewise constant approximation of ${\vect \lambda}_\bcell$ on $\mfaces_{\text{ext}}(T)$.
	Using this in \eqref{mini_flux_dofs}, we get
	\begin{equation}\label{asc_flux_lambda}
		{\vect u}^\text{ext}_\mmesh = \vect A_\mmesh\,\vect C_\mmesh\,\vect R_\mmesh\,{\vect \lambda}_\bcell + {\vect a}_\mmesh.
	\end{equation}
	%The interpolating matrix~$\vect R_\mmesh$ is completely defined by~$n$ and boundary mini\,faces~$\mfaces[ext]$ of~$\mmesh$.
	If we find the mortar vector ~${\vect \lambda}_\bcell$, we recover the local approximation to the face concentration, i.e. ${\vect \lambda}_\mmesh$, from~\eqref{asc_lambda}.
	Further we solve numerically local subproblems in~\eqref{dual_mini} applying the mimetic FD method. This completes the solution algorithm for \eqref{dual}.

	The dimension of the $\Lambda$ space is~$n_\bmesh$, i.e. $(n+1)$ or less unknowns for each face~${F \in \bfaces}$.
	To obtain the system of $n_\bmesh$ equations, we enforce the weak continuity of the moments of  fluxes  on each internal macro-face
	\begin{equation}\label{flux_cont}
		\int_F \vect u|_{\bcell^+}\cdot\hat{\vect n}\,s_i \diff l = \int_F \vect u|_{\bcell^-}\cdot\hat{\vect n}\,s_i \diff l, \quad i = 0, \dots, n, \quad \text{for each } F \in \bfaces[int],
	\end{equation}
	with $\big(\vect u|_{\bcell^+}\cdot\hat{\vect n}\big)(\vect x) = u^\text{ext}_\mmesh(f)\,|f|$, if $\vect x \in f$ for $f\in\mfaces_F(T^+)$, and $u^\text{ext}_\mmesh(f)$ is the local flux assigned to $f$ (component of~$\vect u^\text{ext}_\mmesh$). Similar definition applies to $\vect u|_{\bcell^-}$. 	
	This and~\eqref{asc_flux_lambda} result in the linear algebraic system
	\begin{equation}\label{asc_system}
		\vect S_\bmesh\,{\vect \lambda}_\bmesh = {\vect b}_\bmesh,
	\end{equation}
	with	$\vect S_\bmesh \in \Rn{n_\bmesh \times n_\bmesh}, {\vect \lambda}_\bmesh, {\vect b}_\bmesh \in \Rn{n_\bmesh}$.
	Neumann boundary condition in~\eqref{dual:bc} is handled in the similar way, and Dirichlet boundary data in~\eqref{dual:bc} is enforced strongly in~\eqref{asc_system}.

@@

	We define $\vect R_\mmesh$ locally for any fixed $\bcell\in\bmesh$. Let us enumerate all faces of the given $T$ by index $j$. For example, $j=1,\dots,4$ for the polygonal cell in Figure~\ref{fig:asc_dofs:asc1:mmc}. For each $j$, index $i$ enumerates mini-faces from $\mfaces[ext](T)$ belonging to the macro-face $j$. For example, $i\in\{1,2,3\}$ for $j=1$ and $i\in\{1\}$ for $j=4$ for the same example in Figure~\ref{fig:asc_dofs:asc1:mmc}. Further, denote by $\lambda_{j\,i}(\mmesh)$ the local d.o.f. assigned to the $i$-th mini-face belonging to the $j$-th macro-face, and by $\lambda^{(0)}_{j}(T)$, $\lambda^{(1)}_{j}(T)$ two moments defining an element from $\Lambda$ on the $j$-th macro-face (see Figure~\ref{fig:asc_dofs:asc1:mmc}) so that we have
	\begin{equation}\label{lambda_intermsof_moments}
		{\lambda}\big({\vect r}(t)\big) = \lambda^{(1)}_{j}(T)\,|F|\,t + \left( \lambda^{(0)}_{j}(T) - \frac{\lambda^{(1)}_{j}(T)\,|F|}{2} \right),\qquad  F\in\bfaces[int]
	\end{equation}
	for $\lambda\in\Lambda$. Here $t\in(0,1)$ and ${\vect r}\::\:\left(0,1\right) \rightarrow F$ is the affine parametrization of $F$, which has index $j$ among macro-faces of $T$.
